---
title: "Codebook"
author: "Kari Theobald, Shane Weinstock, Jeremy Simpson, Gabe Gonzales"
date: "4/3/2019"
output:
  html_document:
    keep_md: yes
---
```{r , echo=FALSE, include=FALSE, warning=FALSE, message=FALSE, error=FALSE}
library("ggplot2")
library("pander")
```
```{r 'visualFunctions', echo=FALSE, include=FALSE, warning=FALSE, message=FALSE, error=FALSE}
ggAggHist <- getFromNamespace("ggAggHist", "dataMaid")
ggAggBarplot <- getFromNamespace("ggAggBarplot", "dataMaid")
```
# Data report for Database "Data"
The dataset examined has the following dimensions:


---------------------------------
Feature                    Result
------------------------ --------
Number of observations       1470

Number of variables            35
---------------------------------

# Data report for Database "Small"
The dataset examined has the following dimensions:


---------------------------------
Feature                    Result
------------------------ --------
Number of observations       1470

Number of variables            10
---------------------------------






# Codebook summary table

---------------------------------------------------------------------------
Label   Variable             Class         # unique  Missing  Description  
                                             values                        
------- -------------------- ----------- ---------- --------- -------------
        **[Age]**            numeric             43  0.00 %                

        **[Attrition]**      character            2  0.00 %                

        **[Feq.Travel]**     character            3  0.00 %                

        **[Daily.Rate]**     numeric            886  0.00 %                

        **[Department]**     character            3  0.00 %                

        **[mlg.Home]**       numeric             29  0.00 %                

        **[Education]**      numeric              5  0.00 %                

        **[Ed.Field]**       character            6  0.00 %                

        **[Emp.Count]**      numeric              1  0.00 %                

        **[Emp.Number]**     numeric           1470  0.00 %                

        **[Env.Sat]**        numeric              4  0.00 %                

        **[Gender]**         character            2  0.00 %                

        **[HourlyRate]**     numeric             71  0.00 %                

        **[Job.Invol]**      numeric              4  0.00 %                

        **[Job.Level]**      numeric              5  0.00 %                

        **[Title]**          character            9  0.00 %                

        **[Satisfied]**      numeric              4  0.00 %                

        **[M.S.D]**          character            3  0.00 %                

        **[Income.mos]**     numeric           1349  0.00 %                

        **[Rate.mos]**       numeric           1427  0.00 %                

        **[Jobs.Worked]**    numeric             10  0.00 %                

        **[Over18]**         character            1  0.00 %                

        **[OT]**             character            2  0.00 %                

        **[Percent.Inc]**    numeric             15  0.00 %                

        **[Performance]**    numeric              2  0.00 %                

        **[Sat.Relation]**   numeric              4  0.00 %                

        **[Hours]**          numeric              1  0.00 %                

        **[Stock]**          numeric              4  0.00 %                

        **[Yrs.Wrkd]**       numeric             40  0.00 %                

        **[Training]**       numeric              7  0.00 %                

        **[Work.Life]**      numeric              4  0.00 %                

        **[YOS]**            numeric             37  0.00 %                

        **[YCRole]**         numeric             19  0.00 %                

        **[YbtwnPromo]**     numeric             16  0.00 %                

        **[YwMgmt]**         numeric             18  0.00 %  
        
        **[Attrition]**      factor               2  0.00 %                

        **[Age]**            numeric             43  0.00 %                

        **[Gender]**         factor               2  0.00 %                

        **[M.S.D]**          factor               3  0.00 %                

        **[YOS]**            numeric             37  0.00 %                

        **[Ed.Lvl]**         numeric              5  0.00 %                

        **[Education]**      factor               6  0.00 %                

        **[Title]**          factor               9  0.00 %                

        **[Income.mos]**     numeric           1427  0.00 %                

        **[mlg.Home]**       numeric             29  0.00 % 
---------------------------------------------------------------------------




# Variable list
## Age

<div class = "row">
<div class = "col-lg-8">

-----------------------------------
Feature                      Result
------------------------- ---------
Variable type               numeric

Number of missing obs.      0 (0 %)

Number of unique values          43

Median                           36

1st and 3rd quartiles        30; 43

Min. and max.                18; 60
-----------------------------------


</div>
<div class = "col-lg-4">
```{r 'Var-1-Age', echo=FALSE, fig.width=4, fig.height=3, message=FALSE, warning=FALSE}
ggAggHist(data = structure(list(xmin = c(15L, 20L, 25L, 30L, 
35L, 40L, 45L, 50L, 55L), xmax = c(20L, 25L, 30L, 35L, 40L, 45L, 
50L, 55L, 60L), ymin = c(0, 0, 0, 0, 0, 0, 0, 0, 0), ymax = c(28L, 
95L, 263L, 343L, 276L, 192L, 130L, 96L, 47L)), class = "data.frame", row.names = c(NA, 
-9L)), vnam = "Age")
```
</div>
</div>




---

## Attrition

<div class = "row">
<div class = "col-lg-8">

-------------------------------------
Feature                        Result
------------------------- -----------
Variable type               character

Number of missing obs.        0 (0 %)

Number of unique values             2

Mode                             "No"
-------------------------------------


</div>
<div class = "col-lg-4">
```{r 'Var-2-Attrition', echo=FALSE, fig.width=4, fig.height=3, message=FALSE, warning=FALSE}
ggAggBarplot(data = structure(list(x = structure(1:2, .Label = c("No", 
"Yes"), class = "factor"), y = c(1233L, 237L)), class = "data.frame", row.names = c(NA, 
-2L)), vnam = "Attrition")
```
</div>
</div>


- Observed factor levels: \"No\", \"Yes\". 



---

## Feq.Travel

<div class = "row">
<div class = "col-lg-8">

-------------------------------------------
Feature                              Result
------------------------- -----------------
Variable type                     character

Number of missing obs.              0 (0 %)

Number of unique values                   3

Mode                        "Travel_Rarely"
-------------------------------------------


</div>
<div class = "col-lg-4">
```{r 'Var-3-Feq-Travel', echo=FALSE, fig.width=4, fig.height=3, message=FALSE, warning=FALSE}
ggAggBarplot(data = structure(list(x = structure(1:3, .Label = c("Non-Travel", 
"Travel_Frequently", "Travel_Rarely"), class = "factor"), y = c(150L, 
277L, 1043L)), class = "data.frame", row.names = c(NA, -3L)), 
    vnam = "Feq.Travel")
```
</div>
</div>


- Observed factor levels: \"Non-Travel\", \"Travel_Frequently\", \"Travel_Rarely\". 



---

## Daily.Rate

<div class = "row">
<div class = "col-lg-8">

-------------------------------------
Feature                        Result
------------------------- -----------
Variable type                 numeric

Number of missing obs.        0 (0 %)

Number of unique values           886

Median                            802

1st and 3rd quartiles       465; 1157

Min. and max.               102; 1499
-------------------------------------


</div>
<div class = "col-lg-4">
```{r 'Var-4-Daily-Rate', echo=FALSE, fig.width=4, fig.height=3, message=FALSE, warning=FALSE}
ggAggHist(data = structure(list(xmin = c(100L, 200L, 300L, 400L, 
500L, 600L, 700L, 800L, 900L, 1000L, 1100L, 1200L, 1300L, 1400L
), xmax = c(200L, 300L, 400L, 500L, 600L, 700L, 800L, 900L, 1000L, 
1100L, 1200L, 1300L, 1400L, 1500L), ymin = c(0, 0, 0, 0, 0, 0, 
0, 0, 0, 0, 0, 0, 0, 0), ymax = c(106L, 91L, 103L, 105L, 123L, 
119L, 86L, 107L, 107L, 90L, 111L, 105L, 123L, 94L)), class = "data.frame", row.names = c(NA, 
-14L)), vnam = "Daily.Rate")
```
</div>
</div>




---

## Department

<div class = "row">
<div class = "col-lg-8">

----------------------------------------------------
Feature                                       Result
------------------------- --------------------------
Variable type                              character

Number of missing obs.                       0 (0 %)

Number of unique values                            3

Mode                        "Research & Development"
----------------------------------------------------


</div>
<div class = "col-lg-4">
```{r 'Var-5-Department', echo=FALSE, fig.width=4, fig.height=3, message=FALSE, warning=FALSE}
ggAggBarplot(data = structure(list(x = structure(1:3, .Label = c("Human Resources", 
"Research & Development", "Sales"), class = "factor"), y = c(63L, 
961L, 446L)), class = "data.frame", row.names = c(NA, -3L)), 
    vnam = "Department")
```
</div>
</div>


- Observed factor levels: \"Human Resources\", \"Research & Development\", \"Sales\". 



---

## mlg.Home

<div class = "row">
<div class = "col-lg-8">

-----------------------------------
Feature                      Result
------------------------- ---------
Variable type               numeric

Number of missing obs.      0 (0 %)

Number of unique values          29

Median                            7

1st and 3rd quartiles         2; 14

Min. and max.                 1; 29
-----------------------------------


</div>
<div class = "col-lg-4">
```{r 'Var-6-mlg-Home', echo=FALSE, fig.width=4, fig.height=3, message=FALSE, warning=FALSE}
ggAggHist(data = structure(list(xmin = c(0, 2, 4, 6, 8, 10, 12, 
14, 16, 18, 20, 22, 24, 26, 28), xmax = c(2, 4, 6, 8, 10, 12, 
14, 16, 18, 20, 22, 24, 26, 28, 30), ymin = c(0, 0, 0, 0, 0, 
0, 0, 0, 0, 0, 0, 0, 0, 0, 0), ymax = c(419L, 148L, 124L, 164L, 
171L, 49L, 40L, 58L, 46L, 47L, 37L, 55L, 50L, 35L, 27L)), class = "data.frame", row.names = c(NA, 
-15L)), vnam = "mlg.Home")
```
</div>
</div>




---

## Education

<div class = "row">
<div class = "col-lg-8">

-----------------------------------
Feature                      Result
------------------------- ---------
Variable type               numeric

Number of missing obs.      0 (0 %)

Number of unique values           5

Median                            3

1st and 3rd quartiles          2; 4

Min. and max.                  1; 5
-----------------------------------


</div>
<div class = "col-lg-4">
```{r 'Var-7-Education', echo=FALSE, fig.width=4, fig.height=3, message=FALSE, warning=FALSE}
ggAggHist(data = structure(list(xmin = c(1, 1.5, 2, 2.5, 3, 3.5, 
4, 4.5), xmax = c(1.5, 2, 2.5, 3, 3.5, 4, 4.5, 5), ymin = c(0, 
0, 0, 0, 0, 0, 0, 0), ymax = c(170L, 282L, 0L, 572L, 0L, 398L, 
0L, 48L)), class = "data.frame", row.names = c(NA, -8L)), vnam = "Education")
```
</div>
</div>




---

## Ed.Field

<div class = "row">
<div class = "col-lg-8">

-------------------------------------------
Feature                              Result
------------------------- -----------------
Variable type                     character

Number of missing obs.              0 (0 %)

Number of unique values                   6

Mode                        "Life Sciences"
-------------------------------------------


</div>
<div class = "col-lg-4">
```{r 'Var-8-Ed-Field', echo=FALSE, fig.width=4, fig.height=3, message=FALSE, warning=FALSE}
ggAggBarplot(data = structure(list(x = structure(1:6, .Label = c("Human Resources", 
"Life Sciences", "Marketing", "Medical", "Other", "Technical Degree"
), class = "factor"), y = c(27L, 606L, 159L, 464L, 82L, 132L)), class = "data.frame", row.names = c(NA, 
-6L)), vnam = "Ed.Field")
```
</div>
</div>


- Observed factor levels: \"Human Resources\", \"Life Sciences\", \"Marketing\", \"Medical\", \"Other\", \"Technical Degree\". 



---

## Emp.Count

* The variable only takes one (non-missing) value: \"1\". The variable contains 0 \% missing observations.



---

## Emp.Number

<div class = "row">
<div class = "col-lg-8">

-------------------------------------------
Feature                              Result
------------------------- -----------------
Variable type                       numeric

Number of missing obs.              0 (0 %)

Number of unique values                1470

Median                               1020.5

1st and 3rd quartiles       491.25; 1555.75

Min. and max.                       1; 2068
-------------------------------------------


</div>
<div class = "col-lg-4">
```{r 'Var-10-Emp-Number', echo=FALSE, fig.width=4, fig.height=3, message=FALSE, warning=FALSE}
ggAggHist(data = structure(list(xmin = c(0, 200, 400, 600, 800, 
1000, 1200, 1400, 1600, 1800, 2000), xmax = c(200, 400, 600, 
800, 1000, 1200, 1400, 1600, 1800, 2000, 2200), ymin = c(0, 0, 
0, 0, 0, 0, 0, 0, 0, 0, 0), ymax = c(149L, 144L, 155L, 129L, 
140L, 141L, 136L, 140L, 151L, 137L, 48L)), class = "data.frame", row.names = c(NA, 
-11L)), vnam = "Emp.Number")
```
</div>
</div>




---

## Env.Sat

<div class = "row">
<div class = "col-lg-8">

-----------------------------------
Feature                      Result
------------------------- ---------
Variable type               numeric

Number of missing obs.      0 (0 %)

Number of unique values           4

Median                            3

1st and 3rd quartiles          2; 4

Min. and max.                  1; 4
-----------------------------------


</div>
<div class = "col-lg-4">
```{r 'Var-11-Env-Sat', echo=FALSE, fig.width=4, fig.height=3, message=FALSE, warning=FALSE}
ggAggHist(data = structure(list(xmin = c(1, 1.2, 1.4, 1.6, 1.8, 
2, 2.2, 2.4, 2.6, 2.8, 3, 3.2, 3.4, 3.6, 3.8), xmax = c(1.2, 
1.4, 1.6, 1.8, 2, 2.2, 2.4, 2.6, 2.8, 3, 3.2, 3.4, 3.6, 3.8, 
4), ymin = c(0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0), ymax = c(284L, 
0L, 0L, 0L, 287L, 0L, 0L, 0L, 0L, 453L, 0L, 0L, 0L, 0L, 446L)), class = "data.frame", row.names = c(NA, 
-15L)), vnam = "Env.Sat")
```
</div>
</div>




---

## Gender

<div class = "row">
<div class = "col-lg-8">

-------------------------------------
Feature                        Result
------------------------- -----------
Variable type               character

Number of missing obs.        0 (0 %)

Number of unique values             2

Mode                           "Male"
-------------------------------------


</div>
<div class = "col-lg-4">
```{r 'Var-12-Gender', echo=FALSE, fig.width=4, fig.height=3, message=FALSE, warning=FALSE}
ggAggBarplot(data = structure(list(x = structure(1:2, .Label = c("Female", 
"Male"), class = "factor"), y = c(588L, 882L)), class = "data.frame", row.names = c(NA, 
-2L)), vnam = "Gender")
```
</div>
</div>


- Observed factor levels: \"Female\", \"Male\". 



---

## HourlyRate

<div class = "row">
<div class = "col-lg-8">

-------------------------------------
Feature                        Result
------------------------- -----------
Variable type                 numeric

Number of missing obs.        0 (0 %)

Number of unique values            71

Median                             66

1st and 3rd quartiles       48; 83.75

Min. and max.                 30; 100
-------------------------------------


</div>
<div class = "col-lg-4">
```{r 'Var-13-HourlyRate', echo=FALSE, fig.width=4, fig.height=3, message=FALSE, warning=FALSE}
ggAggHist(data = structure(list(xmin = c(30L, 35L, 40L, 45L, 
50L, 55L, 60L, 65L, 70L, 75L, 80L, 85L, 90L, 95L), xmax = c(35L, 
40L, 45L, 50L, 55L, 60L, 65L, 70L, 75L, 80L, 85L, 90L, 95L, 100L
), ymin = c(0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0), ymax = c(107L, 
84L, 115L, 103L, 104L, 114L, 97L, 93L, 107L, 111L, 113L, 103L, 
104L, 115L)), class = "data.frame", row.names = c(NA, -14L)), 
    vnam = "HourlyRate")
```
</div>
</div>




---

## Job.Invol

<div class = "row">
<div class = "col-lg-8">

-----------------------------------
Feature                      Result
------------------------- ---------
Variable type               numeric

Number of missing obs.      0 (0 %)

Number of unique values           4

Median                            3

1st and 3rd quartiles          2; 3

Min. and max.                  1; 4
-----------------------------------


</div>
<div class = "col-lg-4">
```{r 'Var-14-Job-Invol', echo=FALSE, fig.width=4, fig.height=3, message=FALSE, warning=FALSE}
ggAggHist(data = structure(list(xmin = c(1, 1.2, 1.4, 1.6, 1.8, 
2, 2.2, 2.4, 2.6, 2.8, 3, 3.2, 3.4, 3.6, 3.8), xmax = c(1.2, 
1.4, 1.6, 1.8, 2, 2.2, 2.4, 2.6, 2.8, 3, 3.2, 3.4, 3.6, 3.8, 
4), ymin = c(0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0), ymax = c(83L, 
0L, 0L, 0L, 375L, 0L, 0L, 0L, 0L, 868L, 0L, 0L, 0L, 0L, 144L)), class = "data.frame", row.names = c(NA, 
-15L)), vnam = "Job.Invol")
```
</div>
</div>




---

## Job.Level

<div class = "row">
<div class = "col-lg-8">

-----------------------------------
Feature                      Result
------------------------- ---------
Variable type               numeric

Number of missing obs.      0 (0 %)

Number of unique values           5

Median                            2

1st and 3rd quartiles          1; 3

Min. and max.                  1; 5
-----------------------------------


</div>
<div class = "col-lg-4">
```{r 'Var-15-Job-Level', echo=FALSE, fig.width=4, fig.height=3, message=FALSE, warning=FALSE}
ggAggHist(data = structure(list(xmin = c(1, 1.5, 2, 2.5, 3, 3.5, 
4, 4.5), xmax = c(1.5, 2, 2.5, 3, 3.5, 4, 4.5, 5), ymin = c(0, 
0, 0, 0, 0, 0, 0, 0), ymax = c(543L, 534L, 0L, 218L, 0L, 106L, 
0L, 69L)), class = "data.frame", row.names = c(NA, -8L)), vnam = "Job.Level")
```
</div>
</div>




---

## Title

<div class = "row">
<div class = "col-lg-8">

---------------------------------------------
Feature                                Result
------------------------- -------------------
Variable type                       character

Number of missing obs.                0 (0 %)

Number of unique values                     9

Mode                        "Sales Executive"
---------------------------------------------


</div>
<div class = "col-lg-4">
```{r 'Var-16-Title', echo=FALSE, fig.width=4, fig.height=3, message=FALSE, warning=FALSE}
ggAggBarplot(data = structure(list(x = structure(1:9, .Label = c("Healthcare Representative", 
"Human Resources", "Laboratory Technician", "Manager", "Manufacturing Director", 
"Research Director", "Research Scientist", "Sales Executive", 
"Sales Representative"), class = "factor"), y = c(131L, 52L, 
259L, 102L, 145L, 80L, 292L, 326L, 83L)), class = "data.frame", row.names = c(NA, 
-9L)), vnam = "Title")
```
</div>
</div>


- Observed factor levels: \"Healthcare Representative\", \"Human Resources\", \"Laboratory Technician\", \"Manager\", \"Manufacturing Director\", \"Research Director\", \"Research Scientist\", \"Sales Executive\", \"Sales Representative\". 



---

## Satisfied

<div class = "row">
<div class = "col-lg-8">

-----------------------------------
Feature                      Result
------------------------- ---------
Variable type               numeric

Number of missing obs.      0 (0 %)

Number of unique values           4

Median                            3

1st and 3rd quartiles          2; 4

Min. and max.                  1; 4
-----------------------------------


</div>
<div class = "col-lg-4">
```{r 'Var-17-Satisfied', echo=FALSE, fig.width=4, fig.height=3, message=FALSE, warning=FALSE}
ggAggHist(data = structure(list(xmin = c(1, 1.2, 1.4, 1.6, 1.8, 
2, 2.2, 2.4, 2.6, 2.8, 3, 3.2, 3.4, 3.6, 3.8), xmax = c(1.2, 
1.4, 1.6, 1.8, 2, 2.2, 2.4, 2.6, 2.8, 3, 3.2, 3.4, 3.6, 3.8, 
4), ymin = c(0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0), ymax = c(289L, 
0L, 0L, 0L, 280L, 0L, 0L, 0L, 0L, 442L, 0L, 0L, 0L, 0L, 459L)), class = "data.frame", row.names = c(NA, 
-15L)), vnam = "Satisfied")
```
</div>
</div>




---

## M.S.D

<div class = "row">
<div class = "col-lg-8">

-------------------------------------
Feature                        Result
------------------------- -----------
Variable type               character

Number of missing obs.        0 (0 %)

Number of unique values             3

Mode                        "Married"
-------------------------------------


</div>
<div class = "col-lg-4">
```{r 'Var-18-M-S-D', echo=FALSE, fig.width=4, fig.height=3, message=FALSE, warning=FALSE}
ggAggBarplot(data = structure(list(x = structure(1:3, .Label = c("Divorced", 
"Married", "Single"), class = "factor"), y = c(327L, 673L, 470L
)), class = "data.frame", row.names = c(NA, -3L)), vnam = "M.S.D")
```
</div>
</div>


- Observed factor levels: \"Divorced\", \"Married\", \"Single\". 



---

## Income.mos

<div class = "row">
<div class = "col-lg-8">

---------------------------------------
Feature                          Result
------------------------- -------------
Variable type                   numeric

Number of missing obs.          0 (0 %)

Number of unique values            1349

Median                             4919

1st and 3rd quartiles        2911; 8379

Min. and max.               1009; 19999
---------------------------------------


</div>
<div class = "col-lg-4">
```{r 'Var-19-Income-mos', echo=FALSE, fig.width=4, fig.height=3, message=FALSE, warning=FALSE}
ggAggHist(data = structure(list(xmin = c(0, 2000, 4000, 6000, 
8000, 10000, 12000, 14000, 16000, 18000), xmax = c(2000, 4000, 
6000, 8000, 10000, 12000, 14000, 16000, 18000, 20000), ymin = c(0, 
0, 0, 0, 0, 0, 0, 0, 0, 0), ymax = c(33L, 510L, 371L, 175L, 100L, 
86L, 53L, 16L, 57L, 69L)), class = "data.frame", row.names = c(NA, 
-10L)), vnam = "Income.mos")
```
</div>
</div>




---

## Rate.mos

<div class = "row">
<div class = "col-lg-8">

-----------------------------------------
Feature                            Result
------------------------- ---------------
Variable type                     numeric

Number of missing obs.            0 (0 %)

Number of unique values              1427

Median                            14235.5

1st and 3rd quartiles       8047; 20461.5

Min. and max.                 2094; 26999
-----------------------------------------


</div>
<div class = "col-lg-4">
```{r 'Var-20-Rate-mos', echo=FALSE, fig.width=4, fig.height=3, message=FALSE, warning=FALSE}
ggAggHist(data = structure(list(xmin = c(2000L, 4000L, 6000L, 
8000L, 10000L, 12000L, 14000L, 16000L, 18000L, 20000L, 22000L, 
24000L, 26000L), xmax = c(4000L, 6000L, 8000L, 10000L, 12000L, 
14000L, 16000L, 18000L, 20000L, 22000L, 24000L, 26000L, 28000L
), ymin = c(0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0), ymax = c(110L, 
130L, 123L, 124L, 118L, 116L, 114L, 120L, 117L, 119L, 131L, 99L, 
49L)), class = "data.frame", row.names = c(NA, -13L)), vnam = "Rate.mos")
```
</div>
</div>




---

## Jobs.Worked

<div class = "row">
<div class = "col-lg-8">

-----------------------------------
Feature                      Result
------------------------- ---------
Variable type               numeric

Number of missing obs.      0 (0 %)

Number of unique values          10

Median                            2

1st and 3rd quartiles          1; 4

Min. and max.                  0; 9
-----------------------------------


</div>
<div class = "col-lg-4">
```{r 'Var-21-Jobs-Worked', echo=FALSE, fig.width=4, fig.height=3, message=FALSE, warning=FALSE}
ggAggHist(data = structure(list(xmin = c(0, 1, 2, 3, 4, 5, 6, 
7, 8), xmax = c(1, 2, 3, 4, 5, 6, 7, 8, 9), ymin = c(0, 0, 0, 
0, 0, 0, 0, 0, 0), ymax = c(718L, 146L, 159L, 139L, 63L, 70L, 
74L, 49L, 52L)), class = "data.frame", row.names = c(NA, -9L)), 
    vnam = "Jobs.Worked")
```
</div>
</div>




---

## Over18

* The variable only takes one (non-missing) value: \"Y\". The variable contains 0 \% missing observations.



---

## OT

<div class = "row">
<div class = "col-lg-8">

-------------------------------------
Feature                        Result
------------------------- -----------
Variable type               character

Number of missing obs.        0 (0 %)

Number of unique values             2

Mode                             "No"
-------------------------------------


</div>
<div class = "col-lg-4">
```{r 'Var-23-OT', echo=FALSE, fig.width=4, fig.height=3, message=FALSE, warning=FALSE}
ggAggBarplot(data = structure(list(x = structure(1:2, .Label = c("No", 
"Yes"), class = "factor"), y = c(1054L, 416L)), class = "data.frame", row.names = c(NA, 
-2L)), vnam = "OT")
```
</div>
</div>


- Observed factor levels: \"No\", \"Yes\". 



---

## Percent.Inc

<div class = "row">
<div class = "col-lg-8">

-----------------------------------
Feature                      Result
------------------------- ---------
Variable type               numeric

Number of missing obs.      0 (0 %)

Number of unique values          15

Median                           14

1st and 3rd quartiles        12; 18

Min. and max.                11; 25
-----------------------------------


</div>
<div class = "col-lg-4">
```{r 'Var-24-Percent-Inc', echo=FALSE, fig.width=4, fig.height=3, message=FALSE, warning=FALSE}
ggAggHist(data = structure(list(xmin = 11:24, xmax = 12:25, ymin = c(0, 
0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0), ymax = c(408L, 209L, 
201L, 101L, 78L, 82L, 89L, 76L, 55L, 48L, 56L, 28L, 21L, 18L)), class = "data.frame", row.names = c(NA, 
-14L)), vnam = "Percent.Inc")
```
</div>
</div>




---

## Performance

<div class = "row">
<div class = "col-lg-8">

-----------------------------------
Feature                      Result
------------------------- ---------
Variable type               numeric

Number of missing obs.      0 (0 %)

Number of unique values           2

Median                            3

1st and 3rd quartiles          3; 3

Min. and max.                  3; 4
-----------------------------------


</div>
<div class = "col-lg-4">
```{r 'Var-25-Performance', echo=FALSE, fig.width=4, fig.height=3, message=FALSE, warning=FALSE}
ggAggHist(data = structure(list(xmin = c(3, 3.1, 3.2, 3.3, 3.4, 
3.5, 3.6, 3.7, 3.8, 3.9), xmax = c(3.1, 3.2, 3.3, 3.4, 3.5, 3.6, 
3.7, 3.8, 3.9, 4), ymin = c(0, 0, 0, 0, 0, 0, 0, 0, 0, 0), ymax = c(1244L, 
0L, 0L, 0L, 0L, 0L, 0L, 0L, 0L, 226L)), class = "data.frame", row.names = c(NA, 
-10L)), vnam = "Performance")
```
</div>
</div>




---

## Sat.Relation

<div class = "row">
<div class = "col-lg-8">

-----------------------------------
Feature                      Result
------------------------- ---------
Variable type               numeric

Number of missing obs.      0 (0 %)

Number of unique values           4

Median                            3

1st and 3rd quartiles          2; 4

Min. and max.                  1; 4
-----------------------------------


</div>
<div class = "col-lg-4">
```{r 'Var-26-Sat-Relation', echo=FALSE, fig.width=4, fig.height=3, message=FALSE, warning=FALSE}
ggAggHist(data = structure(list(xmin = c(1, 1.2, 1.4, 1.6, 1.8, 
2, 2.2, 2.4, 2.6, 2.8, 3, 3.2, 3.4, 3.6, 3.8), xmax = c(1.2, 
1.4, 1.6, 1.8, 2, 2.2, 2.4, 2.6, 2.8, 3, 3.2, 3.4, 3.6, 3.8, 
4), ymin = c(0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0), ymax = c(276L, 
0L, 0L, 0L, 303L, 0L, 0L, 0L, 0L, 459L, 0L, 0L, 0L, 0L, 432L)), class = "data.frame", row.names = c(NA, 
-15L)), vnam = "Sat.Relation")
```
</div>
</div>




---

## Hours

* The variable only takes one (non-missing) value: \"80\". The variable contains 0 \% missing observations.



---

## Stock

<div class = "row">
<div class = "col-lg-8">

-----------------------------------
Feature                      Result
------------------------- ---------
Variable type               numeric

Number of missing obs.      0 (0 %)

Number of unique values           4

Median                            1

1st and 3rd quartiles          0; 1

Min. and max.                  0; 3
-----------------------------------


</div>
<div class = "col-lg-4">
```{r 'Var-28-Stock', echo=FALSE, fig.width=4, fig.height=3, message=FALSE, warning=FALSE}
ggAggHist(data = structure(list(xmin = c(0, 0.2, 0.4, 0.6, 0.8, 
1, 1.2, 1.4, 1.6, 1.8, 2, 2.2, 2.4, 2.6, 2.8), xmax = c(0.2, 
0.4, 0.6, 0.8, 1, 1.2, 1.4, 1.6, 1.8, 2, 2.2, 2.4, 2.6, 2.8, 
3), ymin = c(0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0), ymax = c(631L, 
0L, 0L, 0L, 596L, 0L, 0L, 0L, 0L, 158L, 0L, 0L, 0L, 0L, 85L)), class = "data.frame", row.names = c(NA, 
-15L)), vnam = "Stock")
```
</div>
</div>




---

## Yrs.Wrkd

<div class = "row">
<div class = "col-lg-8">

-----------------------------------
Feature                      Result
------------------------- ---------
Variable type               numeric

Number of missing obs.      0 (0 %)

Number of unique values          40

Median                           10

1st and 3rd quartiles         6; 15

Min. and max.                 0; 40
-----------------------------------


</div>
<div class = "col-lg-4">
```{r 'Var-29-Yrs-Wrkd', echo=FALSE, fig.width=4, fig.height=3, message=FALSE, warning=FALSE}
ggAggHist(data = structure(list(xmin = c(0, 5, 10, 15, 20, 25, 
30, 35), xmax = c(5, 10, 15, 20, 25, 30, 35, 40), ymin = c(0, 
0, 0, 0, 0, 0, 0, 0), ymax = c(316L, 607L, 191L, 149L, 109L, 
52L, 33L, 13L)), class = "data.frame", row.names = c(NA, -8L)), 
    vnam = "Yrs.Wrkd")
```
</div>
</div>




---

## Training

<div class = "row">
<div class = "col-lg-8">

-----------------------------------
Feature                      Result
------------------------- ---------
Variable type               numeric

Number of missing obs.      0 (0 %)

Number of unique values           7

Median                            3

1st and 3rd quartiles          2; 3

Min. and max.                  0; 6
-----------------------------------


</div>
<div class = "col-lg-4">
```{r 'Var-30-Training', echo=FALSE, fig.width=4, fig.height=3, message=FALSE, warning=FALSE}
ggAggHist(data = structure(list(xmin = c(0, 0.5, 1, 1.5, 2, 2.5, 
3, 3.5, 4, 4.5, 5, 5.5), xmax = c(0.5, 1, 1.5, 2, 2.5, 3, 3.5, 
4, 4.5, 5, 5.5, 6), ymin = c(0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 
0), ymax = c(54L, 71L, 0L, 547L, 0L, 491L, 0L, 123L, 0L, 119L, 
0L, 65L)), class = "data.frame", row.names = c(NA, -12L)), vnam = "Training")
```
</div>
</div>




---

## Work.Life

<div class = "row">
<div class = "col-lg-8">

-----------------------------------
Feature                      Result
------------------------- ---------
Variable type               numeric

Number of missing obs.      0 (0 %)

Number of unique values           4

Median                            3

1st and 3rd quartiles          2; 3

Min. and max.                  1; 4
-----------------------------------


</div>
<div class = "col-lg-4">
```{r 'Var-31-Work-Life', echo=FALSE, fig.width=4, fig.height=3, message=FALSE, warning=FALSE}
ggAggHist(data = structure(list(xmin = c(1, 1.2, 1.4, 1.6, 1.8, 
2, 2.2, 2.4, 2.6, 2.8, 3, 3.2, 3.4, 3.6, 3.8), xmax = c(1.2, 
1.4, 1.6, 1.8, 2, 2.2, 2.4, 2.6, 2.8, 3, 3.2, 3.4, 3.6, 3.8, 
4), ymin = c(0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0), ymax = c(80L, 
0L, 0L, 0L, 344L, 0L, 0L, 0L, 0L, 893L, 0L, 0L, 0L, 0L, 153L)), class = "data.frame", row.names = c(NA, 
-15L)), vnam = "Work.Life")
```
</div>
</div>




---

## YOS

<div class = "row">
<div class = "col-lg-8">

-----------------------------------
Feature                      Result
------------------------- ---------
Variable type               numeric

Number of missing obs.      0 (0 %)

Number of unique values          37

Median                            5

1st and 3rd quartiles          3; 9

Min. and max.                 0; 40
-----------------------------------


</div>
<div class = "col-lg-4">
```{r 'Var-32-YOS', echo=FALSE, fig.width=4, fig.height=3, message=FALSE, warning=FALSE}
ggAggHist(data = structure(list(xmin = c(0, 5, 10, 15, 20, 25, 
30, 35), xmax = c(5, 10, 15, 20, 25, 30, 35, 40), ymin = c(0, 
0, 0, 0, 0, 0, 0, 0), ymax = c(776L, 448L, 108L, 72L, 41L, 9L, 
12L, 4L)), class = "data.frame", row.names = c(NA, -8L)), vnam = "YOS")
```
</div>
</div>




---

## YCRole

<div class = "row">
<div class = "col-lg-8">

-----------------------------------
Feature                      Result
------------------------- ---------
Variable type               numeric

Number of missing obs.      0 (0 %)

Number of unique values          19

Median                            3

1st and 3rd quartiles          2; 7

Min. and max.                 0; 18
-----------------------------------


</div>
<div class = "col-lg-4">
```{r 'Var-33-YCRole', echo=FALSE, fig.width=4, fig.height=3, message=FALSE, warning=FALSE}
ggAggHist(data = structure(list(xmin = c(0, 2, 4, 6, 8, 10, 12, 
14, 16), xmax = c(2, 4, 6, 8, 10, 12, 14, 16, 18), ymin = c(0, 
0, 0, 0, 0, 0, 0, 0, 0), ymax = c(673L, 239L, 73L, 311L, 96L, 
32L, 25L, 15L, 6L)), class = "data.frame", row.names = c(NA, 
-9L)), vnam = "YCRole")
```
</div>
</div>




---

## YbtwnPromo

<div class = "row">
<div class = "col-lg-8">

-----------------------------------
Feature                      Result
------------------------- ---------
Variable type               numeric

Number of missing obs.      0 (0 %)

Number of unique values          16

Median                            1

1st and 3rd quartiles          0; 3

Min. and max.                 0; 15
-----------------------------------


</div>
<div class = "col-lg-4">
```{r 'Var-34-YbtwnPromo', echo=FALSE, fig.width=4, fig.height=3, message=FALSE, warning=FALSE}
ggAggHist(data = structure(list(xmin = c(0, 1, 2, 3, 4, 5, 6, 
7, 8, 9, 10, 11, 12, 13, 14), xmax = c(1, 2, 3, 4, 5, 6, 7, 8, 
9, 10, 11, 12, 13, 14, 15), ymin = c(0, 0, 0, 0, 0, 0, 0, 0, 
0, 0, 0, 0, 0, 0, 0), ymax = c(938L, 159L, 52L, 61L, 45L, 32L, 
76L, 18L, 17L, 6L, 24L, 10L, 10L, 9L, 13L)), class = "data.frame", row.names = c(NA, 
-15L)), vnam = "YbtwnPromo")
```
</div>
</div>




---

## YwMgmt

<div class = "row">
<div class = "col-lg-8">

-----------------------------------
Feature                      Result
------------------------- ---------
Variable type               numeric

Number of missing obs.      0 (0 %)

Number of unique values          18

Median                            3

1st and 3rd quartiles          2; 7

Min. and max.                 0; 17
-----------------------------------


</div>
<div class = "col-lg-4">
```{r 'Var-35-YwMgmt', echo=FALSE, fig.width=4, fig.height=3, message=FALSE, warning=FALSE}
ggAggHist(data = structure(list(xmin = c(0, 2, 4, 6, 8, 10, 12, 
14, 16), xmax = c(2, 4, 6, 8, 10, 12, 14, 16, 18), ymin = c(0, 
0, 0, 0, 0, 0, 0, 0, 0), ymax = c(683L, 240L, 60L, 323L, 91L, 
40L, 19L, 7L, 7L)), class = "data.frame", row.names = c(NA, -9L
)), vnam = "YwMgmt")
```
</div>
</div>


---

# Variable list
## Attrition

<div class = "row">
<div class = "col-lg-8">

-----------------------------------
Feature                      Result
------------------------- ---------
Variable type                factor

Number of missing obs.      0 (0 %)

Number of unique values           2

Mode                           "No"

Reference category               No
-----------------------------------


</div>
<div class = "col-lg-4">
```{r 'Var-36-Attrition', echo=FALSE, fig.width=4, fig.height=3, message=FALSE, warning=FALSE}
ggAggBarplot(data = structure(list(x = structure(1:2, .Label = c("No", 
"Yes"), class = "factor"), y = c(1233L, 237L)), class = "data.frame", row.names = c(NA, 
-2L)), vnam = "Attrition")
```
</div>
</div>


- Observed factor levels: \"No\", \"Yes\". 



---

## Age

<div class = "row">
<div class = "col-lg-8">

-----------------------------------
Feature                      Result
------------------------- ---------
Variable type               numeric

Number of missing obs.      0 (0 %)

Number of unique values          43

Median                           36

1st and 3rd quartiles        30; 43

Min. and max.                18; 60
-----------------------------------


</div>
<div class = "col-lg-4">
```{r 'Var-37-Age', echo=FALSE, fig.width=4, fig.height=3, message=FALSE, warning=FALSE}
ggAggHist(data = structure(list(xmin = c(15L, 20L, 25L, 30L, 
35L, 40L, 45L, 50L, 55L), xmax = c(20L, 25L, 30L, 35L, 40L, 45L, 
50L, 55L, 60L), ymin = c(0, 0, 0, 0, 0, 0, 0, 0, 0), ymax = c(28L, 
95L, 263L, 343L, 276L, 192L, 130L, 96L, 47L)), class = "data.frame", row.names = c(NA, 
-9L)), vnam = "Age")
```
</div>
</div>




---

## Gender

<div class = "row">
<div class = "col-lg-8">

-----------------------------------
Feature                      Result
------------------------- ---------
Variable type                factor

Number of missing obs.      0 (0 %)

Number of unique values           2

Mode                         "Male"

Reference category           Female
-----------------------------------


</div>
<div class = "col-lg-4">
```{r 'Var-38-Gender', echo=FALSE, fig.width=4, fig.height=3, message=FALSE, warning=FALSE}
ggAggBarplot(data = structure(list(x = structure(1:2, .Label = c("Female", 
"Male"), class = "factor"), y = c(588L, 882L)), class = "data.frame", row.names = c(NA, 
-2L)), vnam = "Gender")
```
</div>
</div>


- Observed factor levels: \"Female\", \"Male\". 



---

## M.S.D

<div class = "row">
<div class = "col-lg-8">

-------------------------------------
Feature                        Result
------------------------- -----------
Variable type                  factor

Number of missing obs.        0 (0 %)

Number of unique values             3

Mode                        "Married"

Reference category           Divorced
-------------------------------------


</div>
<div class = "col-lg-4">
```{r 'Var-39-M-S-D', echo=FALSE, fig.width=4, fig.height=3, message=FALSE, warning=FALSE}
ggAggBarplot(data = structure(list(x = structure(1:3, .Label = c("Divorced", 
"Married", "Single"), class = "factor"), y = c(327L, 673L, 470L
)), class = "data.frame", row.names = c(NA, -3L)), vnam = "M.S.D")
```
</div>
</div>


- Observed factor levels: \"Divorced\", \"Married\", \"Single\". 



---

## YOS

<div class = "row">
<div class = "col-lg-8">

-----------------------------------
Feature                      Result
------------------------- ---------
Variable type               numeric

Number of missing obs.      0 (0 %)

Number of unique values          37

Median                            5

1st and 3rd quartiles          3; 9

Min. and max.                 0; 40
-----------------------------------


</div>
<div class = "col-lg-4">
```{r 'Var-40-YOS', echo=FALSE, fig.width=4, fig.height=3, message=FALSE, warning=FALSE}
ggAggHist(data = structure(list(xmin = c(0, 5, 10, 15, 20, 25, 
30, 35), xmax = c(5, 10, 15, 20, 25, 30, 35, 40), ymin = c(0, 
0, 0, 0, 0, 0, 0, 0), ymax = c(776L, 448L, 108L, 72L, 41L, 9L, 
12L, 4L)), class = "data.frame", row.names = c(NA, -8L)), vnam = "YOS")
```
</div>
</div>




---

## Ed.Lvl

<div class = "row">
<div class = "col-lg-8">

-----------------------------------
Feature                      Result
------------------------- ---------
Variable type               numeric

Number of missing obs.      0 (0 %)

Number of unique values           5

Median                            3

1st and 3rd quartiles          2; 4

Min. and max.                  1; 5
-----------------------------------


</div>
<div class = "col-lg-4">
```{r 'Var-41-Ed-Lvl', echo=FALSE, fig.width=4, fig.height=3, message=FALSE, warning=FALSE}
ggAggHist(data = structure(list(xmin = c(1, 1.5, 2, 2.5, 3, 3.5, 
4, 4.5), xmax = c(1.5, 2, 2.5, 3, 3.5, 4, 4.5, 5), ymin = c(0, 
0, 0, 0, 0, 0, 0, 0), ymax = c(170L, 282L, 0L, 572L, 0L, 398L, 
0L, 48L)), class = "data.frame", row.names = c(NA, -8L)), vnam = "Ed.Lvl")
```
</div>
</div>




---

## Education

<div class = "row">
<div class = "col-lg-8">

-------------------------------------------
Feature                              Result
------------------------- -----------------
Variable type                        factor

Number of missing obs.              0 (0 %)

Number of unique values                   6

Mode                        "Life Sciences"

Reference category          Human Resources
-------------------------------------------


</div>
<div class = "col-lg-4">
```{r 'Var-42-Education', echo=FALSE, fig.width=4, fig.height=3, message=FALSE, warning=FALSE}
ggAggBarplot(data = structure(list(x = structure(1:6, .Label = c("Human Resources", 
"Life Sciences", "Marketing", "Medical", "Other", "Technical Degree"
), class = "factor"), y = c(27L, 606L, 159L, 464L, 82L, 132L)), class = "data.frame", row.names = c(NA, 
-6L)), vnam = "Education")
```
</div>
</div>


- Observed factor levels: \"Human Resources\", \"Life Sciences\", \"Marketing\", \"Medical\", \"Other\", \"Technical Degree\". 



---

## Title

<div class = "row">
<div class = "col-lg-8">

-----------------------------------------------------
Feature                                        Result
------------------------- ---------------------------
Variable type                                  factor

Number of missing obs.                        0 (0 %)

Number of unique values                             9

Mode                                "Sales Executive"

Reference category          Healthcare Representative
-----------------------------------------------------


</div>
<div class = "col-lg-4">
```{r 'Var-43-Title', echo=FALSE, fig.width=4, fig.height=3, message=FALSE, warning=FALSE}
ggAggBarplot(data = structure(list(x = structure(1:9, .Label = c("Healthcare Representative", 
"Human Resources", "Laboratory Technician", "Manager", "Manufacturing Director", 
"Research Director", "Research Scientist", "Sales Executive", 
"Sales Representative"), class = "factor"), y = c(131L, 52L, 
259L, 102L, 145L, 80L, 292L, 326L, 83L)), class = "data.frame", row.names = c(NA, 
-9L)), vnam = "Title")
```
</div>
</div>


- Observed factor levels: \"Healthcare Representative\", \"Human Resources\", \"Laboratory Technician\", \"Manager\", \"Manufacturing Director\", \"Research Director\", \"Research Scientist\", \"Sales Executive\", \"Sales Representative\". 



---

## Income.mos

<div class = "row">
<div class = "col-lg-8">

-----------------------------------------
Feature                            Result
------------------------- ---------------
Variable type                     numeric

Number of missing obs.            0 (0 %)

Number of unique values              1427

Median                            14235.5

1st and 3rd quartiles       8047; 20461.5

Min. and max.                 2094; 26999
-----------------------------------------


</div>
<div class = "col-lg-4">
```{r 'Var-44-Income-mos', echo=FALSE, fig.width=4, fig.height=3, message=FALSE, warning=FALSE}
ggAggHist(data = structure(list(xmin = c(2000L, 4000L, 6000L, 
8000L, 10000L, 12000L, 14000L, 16000L, 18000L, 20000L, 22000L, 
24000L, 26000L), xmax = c(4000L, 6000L, 8000L, 10000L, 12000L, 
14000L, 16000L, 18000L, 20000L, 22000L, 24000L, 26000L, 28000L
), ymin = c(0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0), ymax = c(110L, 
130L, 123L, 124L, 118L, 116L, 114L, 120L, 117L, 119L, 131L, 99L, 
49L)), class = "data.frame", row.names = c(NA, -13L)), vnam = "Income.mos")
```
</div>
</div>




---

## mlg.Home

<div class = "row">
<div class = "col-lg-8">

-----------------------------------
Feature                      Result
------------------------- ---------
Variable type               numeric

Number of missing obs.      0 (0 %)

Number of unique values          29

Median                            7

1st and 3rd quartiles         2; 14

Min. and max.                 1; 29
-----------------------------------


</div>
<div class = "col-lg-4">
```{r 'Var-45-mlg-Home', echo=FALSE, fig.width=4, fig.height=3, message=FALSE, warning=FALSE}
ggAggHist(data = structure(list(xmin = c(0, 2, 4, 6, 8, 10, 12, 
14, 16, 18, 20, 22, 24, 26, 28), xmax = c(2, 4, 6, 8, 10, 12, 
14, 16, 18, 20, 22, 24, 26, 28, 30), ymin = c(0, 0, 0, 0, 0, 
0, 0, 0, 0, 0, 0, 0, 0, 0, 0), ymax = c(419L, 148L, 124L, 164L, 
171L, 49L, 40L, 58L, 46L, 47L, 37L, 55L, 50L, 35L, 27L)), class = "data.frame", row.names = c(NA, 
-15L)), vnam = "mlg.Home")
```
</div>
</div>




---




Report generation information:

 *  dataMaid v1.2.0 [Pkg: 2018-10-03 from CRAN (R 3.5.0)]

 *  R version 3.5.1 (2018-07-02).

 *  Platform: x86_64-apple-darwin15.6.0 (64-bit)(macOS Sierra 10.12.6).

 *  Function call: `makeDataReport(data = Data, mode = c("summarize", "visualize", 
"check"), smartNum = FALSE, file = "codebook_Data.Rmd", replace = TRUE, 
    checks = list(character = "showAllFactorLevels", factor = "showAllFactorLevels", 
        labelled = "showAllFactorLevels", haven_labelled = "showAllFactorLevels", 
        numeric = NULL, integer = NULL, logical = NULL, Date = NULL), 
    listChecks = FALSE, maxProbVals = Inf, codebook = TRUE, reportTitle = "Codebook for Data")`

